% global setting
\setupcolors[state=start]	
\setupinteraction[
state=start,
title={Curriculum Vitae}, 
subtitle={Kathy Xiao's CV},
subject={Curriculum Vitae},
author={Kathy Xiao},
keyword={Curriculum Vitae, Kathy Xiao, Xiao Hongyue, SAP, SAP Labs China, kathy.xiao@sap.com, 肖弘月, 简历}
]
\placebookmarks[subject][subject]
\setupinteractionscreen[option=bookmark]		
\useURL[email][mailto:xhykathy@gmail.com][][xhykathy@gmail.com]

\setuppapersize[A4][A4]
\setuplayout[topspace=0in, bottom=0in, height=12in, edge=0in, backspace=0.6in, width=7in, margin=2.5em]
\setuppagenumbering[location=]
\setupinmargin[align=right]
\setupitemize[1][paragraph, atmargin, unpacked][symbol=a, indentnext=no]
\setupitemize[2][symbol=a][indentnext=no]

\definetypeface[times][rm][serif][times][default][encoding=ec]
\setupbodyfont[times,11pt]
\setupwhitespace[medium]

% customize head
\definehead[CVHEAD][subject]
\setuphead[CVHEAD][width=\hsize, style=\bfa,after={\blank[medium]},number=no]

\definehead[SUBCVHEAD][subject]
\setuphead[SUBCVHEAD][style=\bf,after={\blank[small]},before={\blank[small]},number=no]
%\showframe
\language[en]

\starttext

% title
\midaligned{\framed[frame=off, align=middle]{{\bfa Xiao Hongyue}}}\blank[small]

% contact info
\startalignment[middle]
{+86 135-8565-7196\crlf
 \from[email]}
\stopalignment

\CVHEAD{\framed[width=7in, frame=off, background=color,backgroundcolor=gray, foreground=color,foregroundcolor=black ,align=flushleft]{Experience\hfill\ss{SAP Labs China {\it{2012.4--Present}}}}}
Role 1: {\bf Software Project Management }
\startitemize[joinedup, 1]
\item Organize workshop to analysis project requirement, make project plan and allocate resource.
\item Help colleagues solve block issues in time.
\item Host scrum meetings, including plan, review, retrospect and daily scrum, collect meeting minutes and action items.
\item Track project progress and control risks by agile tools (e.g. Burndown Chart), help the scrum team make deliverables iteratively in each milestone to stakeholders.
\stopitemize
Role 2: {\bf Quality Assurance and Management}
\startitemize[joinedup, 1]
\item Write test cases with product owner, collaborate with designers and developers on end user interaction and implementation details.
\item Test plan management, bug lifecycle management, quality assurance on various KPIs, e.g. performance, language, environment and usability, etc.
\item Host acceptance test for customers and stakeholders, maintain customer relationship, collect potential requirements and improvement for the next phase.
\stopitemize
Role 3: {\bf Customer Engagement and Team Building}
\startitemize[joinedup, 1]
\item Drive customer co-innovation and engagement, arrange customer interview and follow-up.
\item Design user stories, make demo videos both internally and externally, e.g. global conference, customer activities.
\item Organize team activities to build team atmosphere and trust.
\stopitemize

\SUBCVHEAD{Projects}
\startitemize[joinedup, 1]
\item {\it 2017.10--Present~} SAP Extended Warehouse Management, Pack Outbound Deliveries
\item {\it 2016.12--2017.09} SAP Extended Warehouse Management, Pick by Cart
\item {\it 2015.08--2016.10} SAP Transportation Resource Planning 2.0, rail-car solution
\item {\it 2014.05--2015.12} Engineering Change Simulation go-live on Music Group
\item {\it 2013.01--2014.06} Credit Insight co-innovation with ChemChina
\item {\it 2012.02--2012.12} Mobile Workflow Management 1.0 and 2.0 released to Chia Tai Tianqing
\stopitemize

% skills
\SUBCVHEAD{Others}
\startitemize[joinedup,1]
\item Scrum master, design thinking coach, Bikablo/Business Model Development and Innovation course certified.
\item President of dancing club, 200+ active members, help to build positive and health atmosphere for SAP who certified as \quotation{Great Place to Work}, organize dancing classes and annual party, give speeches on behalf of business women and club  in all hands meeting for SAP global executives.
\item Vital ambassador, spokesperson of SAP in magazine and WeChat. 
\item Spot award, early talent mentor.
\stopitemize

% education
\CVHEAD{\framed[width=7in, frame=off, background=color,backgroundcolor=gray, foreground=color,foregroundcolor=black ,align=flushleft]{Education}}
{{\it 2009.09--2012.04}~{\bf Shanghai JiaoTong University}~Master, Software Engineering}\crlf
{{\it 2005.09--2009.06}~{\bf Shanghai University of Electric Power}~Bachelor, Electric Power System and Automation}

\CVHEAD{\framed[width=7in, frame=off, background=color,backgroundcolor=gray, foreground=color,foregroundcolor=black ,align=flushleft]{Language & Skills}}
\startitemize[joinedup,1]
\item {\bf English}: CET-6
\item ISTQB certified Tester
\item JIRA, Microsoft Office, SAP GTP, Bugzilla, Redmine, Camtasia Studio, Photoshop
\item Marathon National first-class athlete, popular chef in XiaChuFang
\stopitemize

\stoptext
